Verifying Demonstrations

### 2017-11-15 contents-poster.tex
Clarifies and shortens first column

    \begin{blueblock}{Scenario: The crowd-counting problem}
      \begin{itemize}
        \item Alice organizes a protest against Eve's regime.
        \item Bob, Carol and others show up.
        \item We want to know how many showed up to support Alice's cause.
      \end{itemize}
    \end{blueblock}

    \begin{figure}
      \includegraphics[width=0.9\linewidth]{fig/Jacobs-method.jpg}
      \caption{%
        Mostly used method, Jacob's method: divide the area into regions, 
        estimate the density in each region, sum them up.
      }
    \end{figure}

    \begin{orangeblock}{Computer vision methods}
      \begin{itemize}
        \item Computer vision does object recognition.
        \item Requires photos/video that cover the entire location, all the time.
        \item This will count people twice.
      \end{itemize}
    \end{orangeblock}

    \begin{orangeblock}{Other methods}
      \begin{itemize}
        \item Scan active mobile phones in the area.
        \item This requires some extra equipment.
        \item This catches bystanders who are not protesting.
      \end{itemize}
    \end{orangeblock}

    \begin{redblock}{Verifying protest participation}
      \begin{itemize}
        \item Alice organizes a protest against Eve's regime.
        \item Bob, Carol and others show up.
        \item {\color{olive!10!green!90} Alice wants to show that many support 
            her cause.}
        \item {\color{red} Eve wants to show that few support Alice's cause.}
        \item It's an adversarial setting!
        \item We need verifiable results.
      \end{itemize}
    \end{redblock}

>>>>

    \begin{blueblock}{Scenario: The crowd-counting problem}
      \begin{itemize}
        \item Alice organizes a protest against Eve's regime.
        \item Bob, Carol and others show up.
        \item Must know how many showed up to support Alice's cause.
      \end{itemize}
    \end{blueblock}

    \begin{orangeblock}{Currently most popular method}
      \centering
      \includegraphics[width=0.9\linewidth]{fig/Jacobs-method.jpg}
      \begin{itemize}
        \item Mostly used method, Jacob's method.
        \item Divide the area into regions, estimate the density in each 
          region, sum them up.
        \item \color{red} Cannot handle cumulative counts.
      \end{itemize}
    \end{orangeblock}

    \begin{orangeblock}{Computer vision methods}
      \begin{itemize}
        \item Computer vision does object recognition.
        \item Requires photos/video that cover the entire location, all the time.
        \item \color{red} This will count people twice.
      \end{itemize}
    \end{orangeblock}

    \begin{orangeblock}{Other methods}
      \begin{itemize}
        \item Scan active mobile phones in the area.
        \item This requires some extra equipment.
        \item \color{red} This catches bystanders who are not protesting.
      \end{itemize}
    \end{orangeblock}

    \begin{redblock}{Verifying protest participation}
      \begin{itemize}
        \item {\color{olive!10!green!90} Alice wants to show that many support 
            her cause.}
        \item {\color{red} Eve wants to show that few support Alice's cause.}
        \item Adversarial setting, requires verifiable results!
      \end{itemize}
    \end{redblock}
